RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2015-01-03 manuscripts/manuscript.Rmd
Edits to Future Directions.

Emerging formats such as the JSON based NeXSON format provide alternate representations of semantic, machine-readable phylogenetic data. At this time, R users must still rely on other tools that can convert these formats into NeXML.
Because the NeXML syntax is extensible, semantic, and machine-readable, this can be done without loss, unlike NEXUS formats.  Nevertheless, a possible future direction would be to provide direct support of such formats through RNeXML or a companion R package.

>>>>

The goals for continued development of `RNeXML` revolve primarily
around three directions. One is better interoperability with other
existing phylogenetic data representations in R, such those found in
the `phylobase` package [@phylobase]. Another is better integration of
the rich metadata semantics found in ontologies defined in the Web
Ontology Language (OWL), including programmatic access to machine
reasoning with such metadata. Finally, and similar to many other R
packages, including those for comparative phylogenetics, in light of
the increasing size of phylogenomic and other datasets mechanisms may
eventually be needed that avoid the requirement to load an entire
file's content into memory.
